\textbf{(b) Unauthorized Access/Misuse of Collected Data}

These cases present privacy risks. In many cases the methods of entry
are the same or similar to traditional computing systems. However, the
privacy risks are elevated due to the pervasiveness of the devices and
the volume of data being collected. Examples:

• FitBit User accounts hacked\footnote{Sara Spary, ``Online Criminals
  Are Targeting Fitbit User Accounts,''.}. This is an example of a
vulnerability that is not particularly new or unique to IoT, it exploits
commonly weak user passwords. However, the type and volume of data
collected by FitBit generates significant privacy implications.

\begin{quote}
• However, researchers have demonstrated the feasibility of capturing
data from the device itself\footnote{Bogdan Carbunar Mahmudur Rahman,
  Madhusudan Banik, ``Fit and Vulnerable: Attacks and Defenses for a
  Health Monitoring Device,'' (Apr 20, 2013).}.
\end{quote}

• TRENDnet - Example of internet-connected video cameras that had very
poor security, despite assurance on the product's website that it was
"secure." This is also one of the first example where the FTC took
action against a consumer-device company for poor security\footnote{https://www.ftc.gov/enforcement/cases-proceedings/122-3090/trendnet-inc-matter}.

• Baby Monitors - Similar to the TrendNet case, these in-home cameras
were built with minimal to no security - allowing very intimate
intrusion of users' privacy\footnote{http://sfglobe.com/2016/01/06/stranger-hacks-familys-baby-monitor-and-talks-to-child-at-night/},\footnote{http://www.zdnet.com/article/security-vulnerability-flaw-internet-things-baby-monitors/}.

• Smart Meters - Research has indicated the many ways that smart meters
can be exploited to violate the privacy of its users\footnote{Kevin L
  Doran, ``Privacy and Smart Grid: When Progress and Privacy Collide,''
  \emph{U. Tol. L. Rev.} 41, (2009): 909.}.

• Automobiles\footnote{Patrick R. Mueller, ``Every Time You Brake, Every
  Turn You Make--- I'll be Watching You: Protecting Driver Privacy in
  Event Data Recorder Information,'' \emph{WIS. L. REV.} 135, (2006):
  138-139.}